External Validation

### 2021-02-03 FEM_R/validation.Rmd
Updated the validation to include Asthma

# Collect the age suffixes into a vector
keep_vars <- c(m_ages, f_ages)
# Now set up the chronic diseases in a list so we can create a bigger list with all of them produced
diseases <- c('hearte', 'hibpe', 'stroke', 'diabe', 'lunge', 'cancre', 'demene')

@@

pivoted.FEM <- pivot_longer(data = FEM,
                            cols = hearte_m_6064:demene_f_100p, 
                            names_to = c('Condition', 'Gender', 'Age_Group'), 
                            names_sep = '_')

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Asthma', Condition != 'Depression', Condition != 'Severe Mental Health Conditions')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)

>>>>

# Collect the age suffixes into a vector
keep_vars <- c(m_ages, f_ages)
# Now set up the chronic diseases in a list so we can create a bigger list with all of them produced
diseases <- c('hearte', 'hibpe', 'stroke', 'diabe', 'lunge', 'cancre', 'demene', 'asthmae')

@@

pivoted.FEM <- pivot_longer(data = FEM,
                            cols = hearte_m_6064:asthmae_f_100p, 
                            names_to = c('Condition', 'Gender', 'Age_Group'), 
                            names_sep = '_')

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Depression', Condition != 'Severe Mental Health Conditions')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)
newFEM$Condition <- gsub("asthmae", "Asthma", newFEM$Condition)
